Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
wip

Before bounding the competitive ratio of \TAlg, we introduce the lemma that upper bounds the cost of a~single repartition of \TAlg.
In our analysis, we distinguish among three types of clusters: $C_1, C_2$ and $C_3$. In a~cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.

>>>>

Before bounding the competitive ratio of \TAlg, we upper-bound the cost of a~single repartition of \TAlg.
In our analysis, we distinguish among three types of clusters: $C_1, C_2$ and $C_3$. In a~cluster of type $C_i$, the size of the largest component contained in this cluster is~$i$.
